### 2016-07-21 Projects/DelCo_2012/Report/DelCo_2012.tex
fix quote error

As pointed out in the results section, the conditions at TC array 3 represented the "best" gas cooling results with the least impact of agents hitting and cooling the thermocouples themselves.

>>>>

As pointed out in the results section, the conditions at TC array 3 represented the ``'best'' gas cooling results with the least impact of agents hitting and cooling the thermocouples themselves.
